Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-30 EMNLP-demo-paper/NLPVis-demo-paper.tex
full paper draft
update abstract
feedback from chris.

\begin{abstract}
Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme. Despite their advantages, the lack of interpretability hinders the deployment and refinement of the model.
%These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
%
In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationship among the input, the model internals (i.e., attention), and the output predictions that in turn shed light on the model decision making processing.

@@

\input{intro.tex}
\input{relatedWorks.tex}
\input{system.tex}
\input{result.tex}

>>>>

\begin{abstract}
Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme. Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models.
%These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
%
In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions which in turn shed light on the model decision-making processing.

@@

\input{intro.tex}
\input{relatedWorks.tex}
\input{system.tex}
\input{result.tex}
\input{conclusion.tex}
